Global phase diagram and possible quantum spin liquid in the extended triangular lattice model

### 2019-12-06 paper/paper.tex
20191206 15:21

\documentclass[aps,prb,reprint,groupedaddress,showpacs,amsfonts,amsmath,amssymb,superscriptaddress]{revtex4-1}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{color}
\usepackage[colorlinks,urlcolor=blue,linkcolor=blue,anchorcolor=blue,citecolor=blue,bookmarks]{hyperref}

@@

\begin{abstract}
\textcolor{red}{Abstract of this article.}

\textcolor{red}{Left blank currently.}
\end{abstract}

@@

\section{Introduction}
Geometric frustration, which arises when the lattice geometry gives rise to constraints that cannot be simultaneously satisfied, plays an important role in various kinds of magnetic systems. In particluar, antiferromagnets on the triangular lattice are typical examples of such geometric frustated spin systems and have attracted numerous interest in condensed matter physics. For nearest-neighbor antiferromagetic Heisenberg model on triangular lattice, Anderson proposed that a fully disordered resonating-valence-bond (RVB) state may be the ground state. However, several theoretical and numerical studies point to a 120$^\circ$ N\'{e}el-ordered ground state. When the next-nearest-neighbor interactions are included which introduce further frustration, the system has a much richer phase diagram incluing a N\'{e}el phase, a phase with spin-wave selection of nontrivial ground states and a phase with incommensurate long-range order. All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system. \textcolor{red}{$\cdots\cdots$}

>>>>

\documentclass[aps,prb,reprint,groupedaddress,showpacs,amsfonts,amsmath,amssymb,superscriptaddress]{revtex4-1}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{color}
\usepackage{changes}
    \definechangesauthor[name={Wang Shi}, color=orange]{swang}

\usepackage[colorlinks,urlcolor=blue,linkcolor=blue,anchorcolor=blue,citecolor=blue,bookmarks]{hyperref}

@@

\begin{abstract}
    The global ground state phase diagram of the Heisenberg-Kitaev-$\Gamma$ model on a triangular lattice is studied using classical Monte Carlo and exact diagonalization. \textcolor{red}{$\cdots \cdots$}
\end{abstract}

@@

\section{Introduction}
Geometric frustration, which arises when the lattice geometry gives rise to constraints that cannot be simultaneously satisfied, plays an important role in various kinds of magnetic systems.
%
\replaced[id=swang]{In particluar, antiferromagnets on the triangular lattice are typical examples of such geometric frustated spin systems and have attracted numerous interest in condensed matter physics. For nearest-neighbor antiferromagetic Heisenberg model on triangular lattice, though a fully disordered resonating-valence-bond (RVB) state was proposed as the possible ground state in the early years, several theoretical and numerical studies point to a 120$^\circ$ N\'{e}el-ordered ground state thereafter. }{The nearest-neighbor spin-$1/2$ antiferromagetic Heisenberg model on triangular lattice is a typical example of such geometric frustrated spin systems and have attracted numerous interest in condensed matter physics. Though a fully disordered resonating-valence-bond (RVB) state was proposed as the possible ground state in the early years, several theoretical and numerical studies point to a 120$^\circ$ N\'{e}el-ordered ground state thereafter.}
%
When the next-nearest-neighbor interactions are included which introduce further frustration, the system has a much richer phase diagram incluing a N\'{e}el phase, a phase with spin-wave selection of nontrivial ground states and a phase with incommensurate long-range order. All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system. \textcolor{red}{$\cdots\cdots$}
